Rotations and Insecticide Resistance initial plots

### 2017-11-22 inst/documents/rotations_notes.Rmd
add min_rwr_interval

*22/11/17*

@@

>>>>

*22/11/17*
~ added sentence about interval 0 RwR to the UI

~ removed this commented out alternative to df_results
  #experimental
  # df_res_active <- data.frame(generation=rep(1:max_gen,n_insecticides),
  #                       insecticide=NA,
  #                       region=NA,
  #                       resistance=NA, stringsAsFactors = FALSE)
  # df_res_refuge <- df_res_active

~ rename rot_count to gens_this_insecticide

@@

~ add in an option to limit switch back to previous insecticides
~ could add something to put a lower limit on length of rotations
